---
title       : 1987 Baseball Season
subtitle    : Results Summary
author      : Renato Leite
job         : Whatever
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : [bootstrap, quiz, shiny, interactive]           
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
ext_widgets : {rCharts: [libraries/polycharts]}
---

## Objective

The app is used to summarize baseball results for games in the 1987 season between 7 teams in the Eastern Division of the American League.

This data is avauable in the package BradleyTerry2

Source:
Page 438 of Agresti, A. (2002) Categorical Data Analysis (2nd Edn.). New York: Wiley.

--- .class #id 

## What it Does

<small>The App does simple operations just to filter some results according to the users interest, first it filters the data, creating a data set only with the games which the home team is the one selected by the user, like in this exemple:

```{r, message=FALSE, echo=FALSE}
library(BradleyTerry2)
library(rCharts)
library(xtable)
```

```{r}
H.team = "Boston"
A.team = "New York"
team.A.home = subset(baseball, baseball$home.team == H.team)
AxB =  subset(team.A.home, team.A.home$away.team == A.team)
names(team.A.home) = c("Home Team" , "Away Team", "Home Team Wins", "Home Team Losses")
```

```{r table, results = 'asis', comment = NA, echo = F}
options(xtable.type = 'html')
xtable(team.A.home)
```
</small>

---

## Plotting

<small>
With the first filter created, the App goes for the away team selected by the user. Selects the right line to creat a bar plot comparing the wins of the teams.

```{r, print=FALSE}
      AvsB = rbind(c(H.team,as.numeric(AxB[3])), c(A.team,as.numeric(AxB[4])))
      AvsB = as.data.frame(AvsB)
      names(AvsB) = c("Team","Wins")
      p = rPlot(x = "Team", y = "Wins", data = AvsB, type = 'bar')
      #p$addParams(dom = 'barPlot')
```
</small>


---

## Result

The last code creats this plot from rCharts that can show if the home team is in advantage.

```{r, results = 'asis', echo=F}
       #p$print('barPlot', include_assets = TRUE, cdn = TRUE)
       p
```

The github with the codes can be foud on [github](http://github.com)




